---
title: "QB Data"
author: "kanyarat Suwannama"
date: "2/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("/Users/kanyaratsuwannama/Desktop/R_Projects/Storytelling/Group Project/Download/NFL Stats")
```

*NO COLLEGE STATS FOR 3 UNDRAFTED (Kurt Warner, Jon Kitna, Jay Fiedler)

```{r}
library(readxl)
library(tidyverse)
library(skimr)
```

load data
```{r}
college_2021 <- read_excel("sportsref_download_2021.xls")
college_2020 <- read_excel("sportsref_download_2020.xls")
college_2019 <- read_excel("sportsref_download_2019.xls") 
college_2018 <- read_excel("sportsref_download_2018.xls")
college_2017 <- read_excel("sportsref_download_2017.xls")
college_2016 <- read_excel("sportsref_download_2016.xls")
college_2015 <- read_excel("sportsref_download_2015.xls")
college_2014 <- read_excel("sportsref_download_2014.xls")
college_2013 <- read_excel("sportsref_download_2013.xls")
college_2012 <- read_excel("sportsref_download_2012.xls")
college_2011 <- read_excel("sportsref_download_2011.xls")
college_2010 <- read_excel("sportsref_download_2010.xls")
college_2009 <- read_excel("sportsref_download_2009.xls")
college_2008 <- read_excel("sportsref_download_2008.xls")
college_2007 <- read_excel("sportsref_download_2007.xls")
college_2006 <- read_excel("sportsref_download_2006.xls")
college_2005 <- read_excel("sportsref_download_2005.xls")
college_2004 <- read_excel("sportsref_download_2004.xls")
college_2003 <- read_excel("sportsref_download_2003.xls")
college_2002 <- read_excel("sportsref_download_2002.xls")
college_2001 <- read_excel("sportsref_download_2001.xls")
college_2000 <- read_excel("sportsref_download_2000.xls")
college_1999 <- read_excel("sportsref_download_1999.xls")
college_1998 <- read_excel("sportsref_download_1998.xls")
college_1997 <- read_excel("sportsref_download_1997.xls")
college_1996 <- read_excel("sportsref_download_1996.xls")
college_1995 <- read_excel("sportsref_download_1995.xls")
college_1994 <- read_excel("sportsref_download_1994.xls")
college_1993 <- read_excel("sportsref_download_1993.xls")
college_1992 <- read_excel("sportsref_download_1992.xls")
college_1991 <- read_excel("sportsref_download_1991.xls")
college_1990 <- read_excel("sportsref_download_1990.xls")
```

remove players drafted 1990 draft or earlier
```{r}
draft_prosp <- draft_prosp %>%
  filter(draft_year > 1990, position == "Quarterback")
```


NA values for round, pick and overall are for players that were undrafted.. some were signed and have nfl stats.  
Undrafted players will be round = 8, pick = 50, overall = 300)
```{r}
draft_prosp$round <- replace_na(draft_prosp$round, 8)
draft_prosp$overall <- replace_na(draft_prosp$overall, 300)
draft_prosp$pick <- replace_na(draft_prosp$pick, 50)
```

remove columns I don't need
```{r}
draft_prosp <- draft_prosp %>%
  select(draft_year, player_id, player_name, school, school_abbr, pick, overall, round, team, team_abbr, guid, weight, height, pos_rk, ovr_rk, grade)
```

```{r}
skim(draft_prosp)
```


remove '+' for HOF designation in NFL data & rename columns
```{r}
nfl_career_passer_rate$Player = str_remove(nfl_career_passer_rate$Player, "[+]")

nfl_career_passer_rate <- nfl_career_passer_rate %>%
  rename(player_name = Player, nfl_pass_rating = Rate)
```

```{r}
skim(nfl_career_passer_rate)
```


rbind college data into one file
```{r}
all_college <- rbind(college_2021, college_2020, college_2019, college_2018, college_2017, college_2016, college_2015, college_2014, college_2013, college_2012, college_2011, 
                     college_2010, college_2009, college_2008, college_2007, college_2006, college_2005, college_2004, college_2003, college_2002, college_2001, college_2000,
                     college_1999, college_1998, college_1997, college_1996, college_1995, college_1994, college_1993, college_1992, college_1991, college_1990)

rm(college_2021, college_2020, college_2019, college_2018, college_2017, college_2016, college_2015, college_2014, college_2013, college_2012, college_2011, 
                     college_2010, college_2009, college_2008, college_2007, college_2006, college_2005, college_2004, college_2003, college_2002, college_2001, college_2000,
                     college_1999, college_1998, college_1997, college_1996, college_1995, college_1994, college_1993, college_1992, college_1991, college_1990)

glimpse(all_college)
```


remove "*" from players names & change column names
```{r}
all_college$Player = str_remove(all_college$Player, "[*]")

all_college <- all_college %>%
  rename(season = Season, rank = Rk, player_name = Player, school = School, conf = Conf, games = G, cmp = Cmp, pass_att = Att...8, cmp_pct = Pct, pass_yds = Yds...10, 
         pass_yds_pa = 'Y/A', adj_pass_yds_pa = 'AY/A', pass_td = TD...13, int = Int, rate = Rate, rush_att = Att...16, rush_yds = Yds...17, avg_rush_yds_pa = Avg, 
         rush_td = TD...19)
```


calculate and add college passer rating and relocate in dataframe
```{r}
all_college <- all_college %>%
  mutate(col_pass_rating = round((((((cmp/pass_att)-.3)*5 + ((pass_yds/pass_att)-3)*.25 + (pass_td/pass_att)*20 + (2.375 - ((int/pass_att)*25))) / 6) *100), 2))

all_college <- all_college %>%
  relocate(col_pass_rating, .before = rush_att)
```

skim all_college
```{r}
skim(all_college) 
```


view top 20 by col-pass_rating
```{r}
all_college %>%
  select(player_name, school, col_pass_rating) %>%
  arrange(desc(col_pass_rating)) %>%
  top_n(20)
```

check for specific player
```{r}
all_college %>%
  filter(player_name == "Tony Romo") %>%
  count()
```




